Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-08-01 writing/nips_submission/response/EML_response.tex
More tweaks

\looseness=-1

@@

\looseness=-1
\textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations. First we clarify how our architecture and training work for learning basic polynomials (see the diagram), then turn to the issue of meta-mappings. As in standard meta-learning, we generate a set of examples, consisting of (input, target) tuples exemplifying the polynomial to be learned. We embed the inputs and targets, then pass them to he meta-network $\mathcal{M}$ which processes them to produce a function embedding. $\mathcal{M}$ concatenates each pair, applies two layers of identical processing to each concatenated pair independently, max pools elementwise across them, and then applies two more layers of processing to produce the function embedding $z^{func}$ for this polynomial. We pass the function embedding through the hyper network $\mathcal{H}$ to parameterize a function $F$ which performs the mapping from inputs to outputs. We can then use $F$ to transform a new set of probe inputs (i.e. points we want to evaluate the polynomial at) to produce a set of predictions, and then train or evaluate the model on corresponding targets. \par 
\looseness=-1

@@

%\looseness=-1

@@

\looseness=-1
\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 62.4\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM. We expect that with more than a few days to tune and refine the model we could do better. \par
\looseness=-1
\textbf{Datasets:} Our tasks will be released on github as stand-alone python modules that other researchers can use. \par
\looseness=-1
\textbf{Language \& continual learning:} In the revised paper we will emphasize the main points before discussing these extensions. We wanted to include language because it provides a simpler way to cue meta-mappings. Specifically, we used the language embedding as input to $\mathcal{H}$ instead of using examples via $\mathcal{M}$. For continual learning, while approaches like LEO generate (and even optimize) task embeddings, we are not aware of prior work that describes the continual learning approach of optimizing only the cached embeddings. Approaches like EWC double the parameter count by adding an ``importance'' parameter for each model parameter. For modern models with up to billions of parameters, caching a relatively low-dimensional task embedding instead could require less memory even up to millions of tasks. 

>>>>

\vspace{-0.1em}\looseness=-1

@@

\vspace{-0.1em}\looseness=-1
\textbf{Approach \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations. First we clarify how our architecture and training work for learning basic polynomials (see the diagram), then turn to the issue of meta-mappings. As in standard meta-learning, we generate a set of examples, consisting of (input, target) tuples exemplifying the polynomial to be learned. We embed the inputs and targets, then pass them to he meta-network $\mathcal{M}$ which processes them to produce a function embedding. $\mathcal{M}$ concatenates each pair, applies two layers of identical processing to each concatenated pair independently, max pools elementwise across them, and then applies two more layers of processing to produce the function embedding $z^{func}$ for this polynomial. We pass the function embedding through the hyper network $\mathcal{H}$ to parameterize a function $F$ which performs the mapping from inputs to outputs. We can then use $F$ to transform a new set of probe inputs (i.e. points we want to evaluate the polynomial at) to produce a set of predictions, and then train or evaluate the model on corresponding targets. \par 
\vspace{-0.1em}\looseness=-1

@@

%\vspace{-0.1em}\looseness=-1

@@

\vspace{-0.1em}\looseness=-1
\textbf{miniImageNet \& datasets:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 62.4\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM. We expect that with more than a few days to tune we could do better. Our tasks will be released on github as stand-alone python modules that other researchers can use. Developing more complex meta-learning datasets which include meta-mappings will be an important direction for future work.\par
\vspace{-0.1em}\looseness=-1
\textbf{Language \& continual learning:} If accepted, our revised paper will emphasize the main points before discussing these extensions. We wanted to include language because it provides a simpler way to cue meta-mappings. Specifically, we used the language embedding as input to $\mathcal{H}$ instead of using examples via $\mathcal{M}$. For continual learning, while approaches like LEO generate (and even optimize) task embeddings, we are not aware of prior work that describes the continual learning approach of optimizing only the cached embeddings. Approaches like EWC double the parameter count by adding an ``importance'' parameter for each model parameter. For modern models with up to billions of parameters, caching a relatively low-dimensional task embedding instead could require less memory even up to millions of tasks. 
